---
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# load library
library(rvest)
library(ggplot2)
library(FinCal)
library(dplyr)
```

```{r echo=FALSE}
stock = "KO"
```

```{r echo=FALSE}
# Custom Functions
# converts values to millions of $
convert <- function(x) {
  x <- gsub('[(]',"-",x)
  x <- gsub('[)]',"",x)
  if (grepl("B", x)) {
    x <- gsub('[B]',"",x) 
    x <- as.double(x)*1e3
  } else if (grepl("M", x)) {
    x <- gsub('[M]',"",x)
    x <- as.double(x)*1
  } else if (grepl("-", x)) {
    x <- gsub('-',"0",x)
    x <- as.double(x)
  }
}

getIncomeData <- function(name) {
  x <- 1
  while (income_names[x] != name) {x<-x+1}
    values <- income_nums[(5*(x-1)+1):(5*x)]
  for(i in 1:5){
    values[i] <- convert(values[i])
  }
  values <- as.numeric(values)
  return(values)
}
getBalanceData <- function(name) {
  x <- 1
  while (balance_names[x] != name) {x<-x+1}
    values <- balance_nums[(5*(x-1)+1):(5*x)]
  for(i in 1:5){
    values[i] <- convert(values[i])
  }
  values <- as.numeric(values)
  return(values)
}
getCashData <- function(name) {
  x <- 1
  while (cash_names[x] != name) {x<-x+1}
    values <- cash_nums[(5*(x-1)+1):(5*x)]
  for(i in 1:5){
    values[i] <- convert(values[i])
  }
  values <- as.numeric(values)
  return(values)
}

getStatsData <- function(name) {
  x<-1
  while (stats_names[x] != name) {x<-x+1}
  value <- stats_nums[x] %>% as.double()
  return(value)
}
```

```{r echo=FALSE}
# Scrape Financial data
income_statement <- paste0('https://www.marketwatch.com/investing/stock/',stock,'/financials')
income_statement_page <- income_statement %>% read_html()
balance_sheet <- paste0('https://www.marketwatch.com/investing/stock/',stock,'/financials/balance-sheet')
balance_sheet_page <- balance_sheet %>% read_html()
cash_flow <- paste0('https://www.marketwatch.com/investing/stock/',stock,'/financials/cash-flow')
cash_flow_page <- cash_flow %>% read_html()
more_stats <- paste0("https://finviz.com/quote.ashx?t=",stock)
more_stats_page <- more_stats %>% read_html()
sp500_page <- "https://www.multpl.com/s-p-500-pe-ratio" %>% read_html()


income_names <- income_statement_page %>% html_nodes(".overflow__cell .fixed--cell") %>% html_text()
income_nums <- income_statement_page %>% html_nodes(".cell__content span") %>% html_text()
balance_names <- balance_sheet_page %>% html_nodes(".overflow__cell .fixed--cell") %>% html_text()
balance_nums <- balance_sheet_page %>% html_nodes(".cell__content span") %>% html_text()
cash_names <- cash_flow_page %>% html_nodes(".overflow__cell .fixed--cell") %>% html_text()
cash_nums <- cash_flow_page %>% html_nodes(".cell__content span") %>% html_text()
stats_names <- more_stats_page %>% html_nodes(".snapshot-td2-cp") %>% html_text()
stats_nums <- more_stats_page %>% html_nodes(".snapshot-td2 b") %>% html_text()
sp500_num <- sp500_page %>% html_nodes("#current") %>% html_text()

#Yearly Data 
Revenue <- getIncomeData("Sales/Revenue")

Equity <- getBalanceData("Total Equity")

Long_Debt <- getBalanceData("Long-Term Debt")

DebtToEquity <- Long_Debt/Equity

Short_Debt <- getBalanceData("Short Term Debt")

Assets <- getBalanceData("Total Assets")

Liabilities <- getBalanceData("Total Liabilities")

CurrentLiabilities <- getBalanceData("Total Current Liabilities")

cash <- getBalanceData("Cash & Short Term Investments")

accountsReceivable <- getBalanceData("Total Accounts Receivable")

Free_Cash_Flow <- getCashData("Free Cash Flow")

NetIncome <- getCashData("Net Income before Extraordinaries")

OperatingMargin <- NetIncome/Revenue

#Valuation data
x<-1
while (income_names[x] != "EPS (Basic)") {x<-x+1}
EPS <- income_nums[(5*x)]
EPS <- as.double(EPS)


PE <- getStatsData("P/E")

price <- getStatsData("Price")

Dividend <- getStatsData("Dividend")

Beta <- getStatsData("Beta")

PEG <- getStatsData("PEG")

x<-1
while (stats_names[x] != "Shs Outstand" ) {x<-x+1}
shsOutstanding <- convert(stats_nums[x])

x<-1
while (stats_names[x] != "Market Cap" ) {x<-x+1}
market_cap <- convert(stats_nums[x])

x<-1
while (stats_names[x] != "Dividend %") {x<-x+1}
Dividend_Percent <- stats_nums[x]
Dividend_Percent <- as.numeric(sub("%", "", Dividend_Percent))/100


```

```{r echo=FALSE}
library(stringr)
sp500PE <- str_extract(sp500_num, "(\\d\\d)\\.(\\d\\d)") %>% as.double()
```





```{r echo=FALSE}
## Intrinsic Value Functions

r = (PE/PEG)/100

market_debt <- function(short, long) {
  mean(tail(short, 2)) + mean(tail(long, 2))
}


dcf_analysis <- function(Free_Cash_Flow, shsOutstanding) {
  a <- Free_Cash_Flow[5]
  for (i in 1:8) {
    a[i+1] <- (a[i]+a[i]*r)
  }
  dcf <- sum(a)-a[1]
  return(dcf/shsOutstanding)
}

dividend_analysis <- function(Dividend, r) {
  Dividend/(0.08 - r)
}


fm_analysis <- function(PE, r, EPS) {
  EPS * (1 + r) * PE
}

intrinsic_value <- fm_analysis(PE, r, EPS)


asset_based <- function(assets, liabilities, shsOutstanding) {
  (tail(assets, 1) - tail(liabilities, 1))/shsOutstanding
}
```
```{r, echo=FALSE}
df <- data.frame (
  year = 1:5,
  Revenue = Revenue,
  DebtToEquity = DebtToEquity,
  Free_Cash_Flow = Free_Cash_Flow,
  Equity = Equity,
  Debt = Long_Debt,
  OperatingMargin = OperatingMargin
)
```
```{r echo=FALSE}
score <- 0

delm <- lm(DebtToEquity ~ year, df)
if(coef(delm)[2] < 0) {score = score + 1}

rlm <- lm(Revenue ~ year, df)
if(coef(rlm)[2] > 0) {score = score + 1}

omlm <- lm(OperatingMargin ~ year, df)
if(coef(rlm)[2] > 0) {score = score + 1}

quick <- quick.ratio(cash[5],0,accountsReceivable[5],CurrentLiabilities[5])
if(quick > 1) {score = score + 1}

financial_health_grade <- case_when(
  score == 0 ~ "F",
  score == 1 ~ "D",
  score == 2 ~ "C",
  score == 3 ~ "B",
  score == 4 ~ "A"
)
```

# Stock Analysis of `r stock`

## Price Valuations

**Current Price:** `r price`  
**Financial Metric Valuation:** `r round(fm_analysis(PE, r, EPS),2)`  
**Asset Based Valuation:** `r round(asset_based(Assets, Liabilities, shsOutstanding),2)`  
**DCF Valuation**: `r round(dcf_analysis(Free_Cash_Flow, shsOutstanding),2)`

## Important Numbers 

```{r echo = FALSE}
BetaValue = ifelse(Beta > 1, "more volatile", "less volatile")
PEValue = ifelse(PE > sp500PE, "more pricy", "less pricy")
```

**Beta:** `r Beta`  
**S&P500 Average Beta:** 1  
**Note:** `r stock` is `r BetaValue` than the S&P500 

**P/E:** `r PE`  
**S&P500 Average PE:** `r sp500PE`  
**Note:** `r stock` is `r PEValue` than the S&P500

Financial Health Grade: `r financial_health_grade`

## Plots

### Revenue Plot  

```{r echo=FALSE}
graph <- function(data,col,ylabel) {
    ggplot(df, aes(year,data)) +
      geom_bar(stat="identity", width = 0.8, fill = col, color = "black", alpha = 0.8) +
      #geom_smooth(method=lm, se=FALSE, size=2) +
      geom_text(aes(label=data), vjust = -0.3) +
      ylab(ylabel) +
      theme_bw()
}

graph(Revenue, "forestgreen","Revenue in Millions of $")

```
Revenue is how much a company makes from selling goods/services. Provides insight into how much a company is growing. A good sign is if revenue is positive and grows every year.

### Free Cash Flow Plot  

```{r echo=FALSE}
graph(Free_Cash_Flow, "purple","Free Cash Flow in Millions of $")
```
Free Cash Flow is how much cash a company has at its disposal. A positive and growing amount of free cash flow is a great sign for a company


### Debt vs Equity plot    

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df, aes(x = year, y = Equity)) +
  geom_col(aes(fill = "Equity"), 
           color = "black",
           width = 0.45,
           position = position_nudge(x = -0.225)) +
  geom_col(aes(y = Long_Debt, fill = "Long Term Debt"), 
           color = "black",
           width = 0.45,
           position = position_nudge(x = 0.225)) +
  scale_fill_manual(values = alpha(c("blue", "red"), .8)) +
  ylab("Equity vs Long Term Debt (in Millions of $)") +
  theme_bw()

```
Shareholder equity represents the net worth of a company while the long-term debt represents how much a company owes beyond one year. This graph shows the scale between how much a company is worth vs how much they owe in debt. 

### Debt-to-Equity Ratio Plot  

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df, aes(year, DebtToEquity)) +
  geom_smooth(col = "#B80F0A") +
  #geom_line(col="#B80F0A", size = 2) +
  geom_point(size=4, col="#B80F0A") +
  geom_text(label=round(DebtToEquity,2), y=DebtToEquity+.07) +
  geom_hline(yintercept = 1) +
  annotate("text", x=2, y=1.05, label='"Good" Debt to Equity') +
  ylim(0,max(1.5,DebtToEquity)) +
  theme_bw()
```
Debt-to-Equity is calculated by dividing a company's long-term debt by its shareholders' equity. Represents  a company's reliance on debt to fund their operations


